Draft

### 2020-07-28 Draft.Rmd
re-arrange the structure of the draft, add new texts content

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes: usepackage{amsmath}
output:
  pdf_document:
    fig_height: 3
    fig_width: 4
---

@@

Specific simulation scenarios are listed as follows ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom):

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

@@

### 2.2.3 Simulation results

@@

From Table 3. we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case. These results are consistent with conclusions from (Loiaza-Maya et al., 2020). It simply means that we can improve prediction accuracy in the presence of model misspecification ?? , and gain more from using optimal forecasts method while the degree of model misspecification is high.

@@

# Score trace for simulation

As stated in previous literature, focused score

```{r, out.width="600px",fig.align='center'}
knitr::include_graphics("figure 1.pdf")
```

```{r, out.width="600px",fig.align='center'}
# knitr::include_graphics("figure 2.pdf")
```

# Probabilistic density over time 
### 6.1.3 Predictive Densities

The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecast matches the shape of true DGP distribution at diﬀerent time.

```{r, out.width="600px"}
knitr::include_graphics("figure 3.png")
```

```{r, out.width="600px"}
knitr::include_graphics("figure 4.png")
```

```{r, out.width="600px"}
knitr::include_graphics("figure 5.png")
```

```{r, out.width="600px"}
knitr::include_graphics("figure 6.png")
```

```{r, out.width="600px"}
knitr::include_graphics("figure 7.png")
```

```{r, out.width="600px"}
knitr::include_graphics("figure 8.png")
```

# Value-at-Risk

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F,booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table 7: Value-at-Risk when true DGP is copula (shape = -5)"=5))
```

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table 8: Value-at-Risk when true DGP is GARCH(1,1) with degree of freedom = 3"=5))
```

# Empirical Analysis
## S&P500

@@

@@

##### Average scores

@@

The average score table, similar to simulation analysis, is produced for daily logarithmic returns of S&P500. For example, in column 4 (FSR10), a focused score at 10% will produce the optimal prediction in terms of forecasting the 10% tail of the returns’ distribution. The results in this table indicate that we expect to gain considerably from optimal probabilistic forecasts in practice.

##### Score traces

@@

# VaR analysis of S&P500

#### Table 11: Before 2008 GFC

@@

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table ?: VaR for S&P500 before GFC"=5))

@@

#### Table 12: After 2008 GFC

@@

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table ?: VaR for S&P500 after GFC"=5))

@@

## VIX

@@

>>>>

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes: usepackage{amsmath}
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
---

@@

Specific simulation scenarios are listed in following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\multicolumn{3}{|c|}{Simulation design} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

@@

### 2.2.3 Simulation results
#### 2.2.3.1 Average score tables

@@

From Table 3. we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case. These results are consistent with conclusions from (Loiaza-Maya et al., 2020). It simply means that we can improve prediction accuracy in the presence of model misspecification ?? , and gain more from using optimal forecasts method while the degree of model misspecification is high. In other words, we are expected to gain more from using focused score when we observe 'strict coherence' while comparing two forecasts.

@@

#### 2.2.3.2 Score traces plots

As stated in previous literature, focused score tends to outperform CRPS and logarithmic score in predicting tails. Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in figure 1 and 2. In the left panel, it shows the performance of each score evaluated by FSR 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From figure 1 and 2, we could see that FSR makes no difference if the degree of model misspecification is very small but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails. The more misspecified the model is, the more benefits can we gain from using FSR. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model in the fact that in practice, a correct model does not exist.

```{r}
# need to adjust the size. 
knitr::include_graphics("figure 1.pdf")
```

```{r}
knitr::include_graphics("figure 2.pdf")
```

Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots. They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and therefore, outperform predictions from using LS.

## 2.3 Empirical analysis

From the results in section 2.2, we can conclude that optimal forecasts based on focused score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification. In section 2.3, we apply this method to an empirical setting and investigate how it performs in practice.

The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a time period that precedes the 2008 Global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacts on financial market. The methodology used here is the same as in the section 2.2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.

### 2.3.1 Empirical analysis results

@@

```{r,message=FALSE,fig.align="center"}

@@

The descriptive statistics shows that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation. Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.

The reality is always the most complicated and the underlying ARCH(1) should have a high degree of model misspecification. Therefore, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution. The results of Table 9 support our conjecture. However, the difference between using FSR10(80) and FSR20(90) is very small.

@@

Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some important events. In figure 12, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE in terms of predicting both upper and lower tails. And this 'jump' effect continues until the very recent date. It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulance, which could represent a great contribution to the existing financial analyses of risks and returns.

@@

# 3. Finanical application: Value-at-Risk
## 3.1 Overview of Value-at-Risk

## 3.2 Value-at-Risk for simulation analysis
We illustrate our Value-at-Risk analysis by firstly using simulation data from section 2.

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F,booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table 7: VaR when true DGP is copula (shape = -5)"=5))
```

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table 8: VaR when true DGP is GARCH with degree of freedom = 3"=5))
```

## 3.3 Value-at-Risk for empirical analysis

@@

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table 11: VaR for S&P500 before GFC"=5))

@@

@@

df %>% 
  mutate(
    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
  add_header_above(c("Table 12: VaR for S&P500 after GFC"=5))

@@

# 4. VIX analysis 
## 4.1 Background and notation

Previously, we investigate how scoring rules perform in predicting financial returns and volatility. However, the volatility modelled/simulated in (G)ARCH models are ...

VIX is different from volatility modelled through any models. It is a measure for implied volatility, which is non-parametric.

## 4.2 Model specification

The difference and similarity between realised volatility and VIX. why we can use model for RV to model VIX.

@@

# Appendix 
## Appendix 1: Predictive Densities

The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecast matches the shape of true DGP distribution through the simulation. Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in figure 3 to 8. The blue line is the marginal distribution from the true DGP, and these figures show that predictive density produced from optimizing LS fits the area with high probability mass the best, which is also what LS is designed for. However, it performs poorly in terms of predicting tails when the degree of model misspecification is high in both GARCH and copula examples. This is when we benefit from using focused score, and we can see from figure 5 and 8 that predictions produced from optimizing focused score aim to match the shape of two tails of the true distribution. They outperform predictions from using Maximum likelihood estimation (MLE).

```{r}
knitr::include_graphics("figure 3.pdf")
```

```{r}
knitr::include_graphics("figure 4.pdf")
```

```{r}
knitr::include_graphics("figure 5.pdf")
```

```{r}
knitr::include_graphics("figure 6.pdf")
```

```{r}
knitr::include_graphics("figure 7.pdf")
```

```{r}
knitr::include_graphics("figure 8.pdf")
```
